Quantum Interval-Valued Probability: Measurement and Probability

### 2017-08-29 prop_iop.tex
prop_iop.tex \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability Measures\label{subsec:Quantum-I_D-valued-Probability}} Editing equations...

Let $\events'_{j}$ be the subspace of events induced by $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$.
Clearly, $\events'_{j}\subseteq\widehat{\events}$. Therefore, restricting
$\tau$ on each $\events'_{j}$ gives a function\nb$\tau|_{\events'_{j}}:\events'_{j}\rightarrow2^{\Omega}$.
Then, we can follow lemma~\ref{lemma:observable2random-variable}
to induce random variables\nb$X_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }$,
and have $\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\int X_{j}\rmd\bar{\mu}'$
by lemma~\ref{lemma:interval-expectation-value-between-classical-quantum}.
Therefore, 
\begin{eqnarray*}
 &  & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\prod_{j}\int X_{j}\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-product}}{=} & \int\prod_{j}X_{j}\rmd\bar{\mu}'=\int\prod_{j}\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'\\
 & = & \int\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'=\expval{\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}}_{\bar{\mu}}\\
 & = & \expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.
\end{eqnarray*}
\end{proof}

\begin{proof}[Proof 2]Since $\left\{ \mathbf{O}_{j}\right\} $ is
a sequence of commuting observables, they can be diagonalized by a
common orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$,
i.e., $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$ and
$\prod_{j}\mathbf{O}_{j}=\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}$.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one $\proj{k}$
such that $\mu\left(\proj{k}\right)=1$.
\begin{eqnarray*}
 &  & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} \\
 & = & \prod_{j}\left\{ \lambda_{j,k}\right\} =\left\{ \prod_{j}\lambda_{j,k}\right\} \\
 & = & \expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.
\end{eqnarray*}
\end{proof}

>>>>

Let $\events'_{j}$ be the subspace of events induced by $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$.
Clearly, $\events'_{j}\subseteq\widehat{\events}$. Therefore, restricting
$\tau$ on each $\events'_{j}$ gives a function\nb$\tau|_{\events'_{j}}:\events'_{j}\rightarrow2^{\Omega}$.
Then, we can follow lemma~\ref{lemma:observable2random-variable}
to induce random variables\nb$X_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }$,
and have $\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\int X_{j}\rmd\bar{\mu}'$
by lemma~\ref{lemma:interval-expectation-value-between-classical-quantum}.
Therefore, 
\begin{equation}\eqalign{ 
 & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\prod_{j}\int X_{j}\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-product}}{=}\int\prod_{j}X_{j}\rmd\bar{\mu}'\\
= & \int\prod_{j}\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'=\int\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'\\
= & \expval{\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,. 
}\end{equation}
\end{proof}

\begin{proof}[Proof 2]Since $\left\{ \mathbf{O}_{j}\right\} $ is
a sequence of commuting observables, they can be diagonalized by a
common orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$,
i.e., $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$ and
$\prod_{j}\mathbf{O}_{j}=\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}$.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one $\proj{k}$
such that $\mu\left(\proj{k}\right)=1$.
\begin{equation}\eqalign{ 
 & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} =\prod_{j}\left\{ \lambda_{j,k}\right\} \\
= & \left\{ \prod_{j}\lambda_{j,k}\right\} =\expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,. 
}\end{equation}
\end{proof}
